On the presentation of orthogonal groups over polynomial rings

### 2019-08-14 dl-paper.tex
Minor fix

%\subsection{Construction of a model for $\St(\Phi, A[X\inv] + M[X])$}
\subsection{Proof of the $\mathbb{P}^1$-glueing theorem.} \label{sec:P1glueing}
Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise. Let $A$ be a local ring with maximal ideal $M$ and residue field $k$. As in~\cref{firstPart} we denote by $B$ the ring $A[X\inv] + M[X]$ considered as a graded subring of the ring of Laurent polynomials $R = A[X, X\inv]$.

@@

We are ready to prove the key result of this subsection.
\begin{theorem}
 Let $\Phi$ be a root system of type $\rA_{\geq 4}, \rD_{\geq 5}$ or $\rE_{6,7,8}$.
 Suppose that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, A[X, X\inv])$ is injective.  
 Then the map $j_-$ is injective and the following commutative square is pullback
 \begin{equation} \nonumber
  \xymatrix{ \St(\Phi, A) \ar[r] \ar[d] & \St(\Phi, A[X]) \ar[d]^{j_+} \\ \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, A[X, X\inv]).}
 \end{equation}
\end{theorem}
\begin{proof} Since $j_- = j_R j_B^-$, where $j_B^-$ is as in~\cref{prop43}, it suffices to show that $j_B^-$ is injective.
 Set $v_0 = [1, 1, 1] \in \overline{V}$ and suppose $g \in \Ker(j_B)$.
 By~\cref{prop43} holds $v_0 = j_B(g) \cdot v_0 = [1, g, 1]$ therefore $g \in G_M^0$ and consequently $g = 1$.

@@

 Set $h_+ = g_+g_0^{-1}$ and $h_- = g_-g_0^{-1}$, $v_0 = (1, [j_-(h_-)], 1)$.
 It is clear that $h_+ \in \overline{\St}(\Phi, A[X], M[X])$, $h_- \in \overline{\St}(\Phi, A[X\inv], M[X\inv])$ and that $j_-(h_-) = j_+(h_+)$.
 From~\cref{prop43} and~\cref{lem:action} we obtain that
 \[ [j_+(h_+)^{-1}, h_-, 1] = j_+(h_+)^{-1} \cdot [1, h_-, 1] = j_+(h_+)^{-1} j_B^-(h_-) \cdot [1, 1, 1] = [1, 1, 1]. \]
 Thus, $h_-$ (and hence $h_+$) come from some element of $G_M^0$, which implies that $g_+$ and $g_-$ are images of some element of $\St(\Phi, A)$.
 \end{proof}

>>>>

\subsection{Proof of the $\mathbb{P}^1$-glueing theorem.} \label{sec:P1glueing}
Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise. Let $A$ be a local ring with maximal ideal $M$ and residue field $k$. As in~\cref{firstPart} we denote by $B$ the ring $A[X\inv] + M[X]$ considered as a graded subring of the ring of Laurent polynomials $R = A[X, X\inv]$.

@@

We are ready to prove the key result of this section.
\begin{theorem}
 Let $\Phi$ be a root system of type $\rA_{\geq 4}, \rD_{\geq 5}$ or $\rE_{6,7,8}$.
 Suppose that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, A[X, X\inv])$ is injective.  
 Then the map $j_-$ is injective and the following commutative square is pullback
 \begin{equation} \nonumber
  \xymatrix{ \St(\Phi, A) \ar[r] \ar[d] & \St(\Phi, A[X]) \ar[d]^{j_+} \\ \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, A[X, X\inv]).}
 \end{equation}
\end{theorem}
\begin{proof} Since $j_- = j_R j_B^-$, where $j_B^-$ is as in~\cref{prop43}, it suffices to show that $j_B^-$ is injective.
 Set $v_0 = [1, 1, 1] \in \overline{V}$ and suppose $g \in \Ker(j_B)$.
 By~\cref{prop43} holds $v_0 = j_B(g) \cdot v_0 = [1, g, 1]$ therefore $g \in G_M^0$ and consequently $g = 1$.

@@

 Set $h_+ = g_+g_0^{-1}$ and $h_- = g_-g_0^{-1}$.
 It is clear that \[ h_+ \in \overline{\St}(\Phi, A[X], M[X]), h_- \in \overline{\St}(\Phi, A[X\inv], M[X\inv])\text{ and that }j_-(h_-) = j_+(h_+).\]
 From~\cref{prop43} and~\cref{lem:action} we obtain that
 \[ [j_+(h_+)^{-1}, h_-, 1] = j_+(h_+)^{-1} \cdot [1, h_-, 1] = j_+(h_+)^{-1} j_B^-(h_-) \cdot [1, 1, 1] = [1, 1, 1]. \]
 Thus, $h_-$ (and hence $h_+$) come from some element of $G_M^0$, which implies that $g_+$ and $g_-$ are images of some element of $\St(\Phi, A)$.
 \end{proof}
